
\documentclass[12pt,article]{memoir}

\begin{document}

\chapter*{Basic font selection}

This document is not about choosing different default fonts. It's simply about what you can do with what you've got. You shouldn't have to use these commands much. If you want to emphasise what you're saying, use the \verb|\emph{}| command. That should be all you need in prose.

\section*{Font sizes}

It's important to use these commands to choose your fontsize so that if you ever change the base font size of your document (with a class option), your larger things will scale appropriately:

\begin{center}
	\tiny tiny
	\scriptsize scriptsize
	\footnotesize footnotesize
	\small small
	\normalsize normalsize
	
	\large large
	\Large Large
	\LARGE LARGE
	\huge huge
	\Huge Huge
\end{center}

\section*{Matching alternate fonts}

You may have noticed that I use a number of different fonts for things in this document. They are all part of the same super-family ``Computer Modern'', so they are designed to blend together nicely. See Table~\ref{tab:cm} for a list of every font you may possibly choose by default.

\begin{table}[htbp]
\centering
\begin{tabular}{@{}ccc@{\hspace{2em}}>{\ttfamily}c>{\ttfamily}c@{}}
\toprule
\multicolumn{3}{c}{Font description} & \multicolumn{2}{c}{LaTeX command}\\
\cmidrule(r){1-3}\cmidrule{4-5}
Family & Series & Shape & \normalfont Closed & \normalfont Open\\
\midrule
Roman & Regular & Upright  & textrm & rmfamily \\
& & \itshape Italic & textit & itshape \\
& & \slshape Slanted & textsl & slshape  \\
& & \scshape Small Caps & textsc & scshape \\
& \bfseries Bold & \bfseries Upright & textbf & bfseries \\
& & \bfseries  \itshape Italic & \multicolumn{2}{c}{\ttfamily\emph{bf \& it}} \\
& & \bfseries  \slshape Slanted  & \multicolumn{2}{c}{\ttfamily\emph{bf \& sl}} \\
\midrule
\sffamily San Serif & \sffamily Regular & \sffamily Upright & textsf & sffamily \\
& & \sffamily \slshape Slanted  & \multicolumn{2}{c}{\ttfamily\emph{sf \& sl}}\\
& \sffamily \bfseries Bold & \sffamily \bfseries Upright  &\multicolumn{2}{c}{\ttfamily\emph{sf \& bf}} \\
\midrule
\ttfamily Typewriter & \ttfamily Regular & \ttfamily Upright & texttt & ttfamily \\
& & \ttfamily \itshape Italic  &\multicolumn{2}{c}{\ttfamily\emph{tt \& it}} \\
& & \ttfamily \slshape Slanted  & \multicolumn{2}{c}{\ttfamily\emph{tt \& sl}} \\
& & \ttfamily \scshape Small Caps  & \multicolumn{2}{c}{\ttfamily\emph{tt \& sc}} \\
\bottomrule
\end{tabular}
\caption{The Computer Modern font families. Italics are abbreviations meaning combinations of commands given above them.}
\label{tab:cm}
\end{table}

There are two forms of font-choosing commands. The first is as I've used in the source for Table~\ref{tab:cm}: \verb|{\slshape slanted}| to typeset {\slshape slanted} (more often known as oblique); \verb|{\bfseries bold}| to typeset {\bfseries bold}; etc.

The other method is for changing short amounts of text at a time, and the commands are less complex than those above. \verb|\textsf{sans serif}| will result in \textsf{sans serif}; \verb|\textsc{Small Caps}| will give \textsc{Small Caps}; etc.

\end{document}